---
title: "Data Visualization Final"
author: "Patrick Doyle"
date: "March 10, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages('jsonlite')
# install.packages('anytime')
# install.packages('ggplot2')
# install.packages('plotly')
# install.packages('shiny')
# install.packages("shinythemes")
source('global.R')
source('gradleCharts.R')
```

## Data Visualization
### Patrick Doyle - Dr. Finegold - Merrimack College
March 2018 - Final Dashboard

The purpose of this project was to create a dashboard for the Configuration Management team at IDEXX Labratories.  They have recently starting using the *Gradle build environment* platform for building embedded devices.  There is an API built into it that allows for data extraction and a *Golang* application was written and zipped up as part of this project to display the effort put into obtaining and cleaning data for a meaningful visualization in the business world.  

The project was open ended for two of the three visualizations. The *Plugin* visualization had business requirements that were asked for.  The other two plots were up to the author to create something meaningful and hopefully useful.

```{r buildTimesChart}
generateBuildTimesChart(pluginsListing)
```

```{r cars}
summary(cars)
```

```{r cars}
summary(cars)
```

```{r cars}
summary(cars)
```

```{r cars}
summary(cars)
```

```{r cars}
summary(cars)
```